Project 1 Checkpoint

### 2015-02-03 project1/checkpoint/main.tex
Finishing up conceptual model
Adding a little more text

The car model will listen for this event as well. When a currently traveling car sees a red light, it will calculate
\emph{where} it needs to stop, and \emph{when} it will come to a stop. This will be done using a deceleration model
similar to \cite{deceleration}.

@@

We first concern ourselves with finding an input distribution for cars entering the system. In our model, we'll only
consider the car arrival time, and car length when modeling cars. Due to the discrete nature of the application, we'll
ignore some of the more "continuous" aspects, such car velocity and acceleration and encompass them into calculation
of event times.

>>>>

The car model will listen for this event as well. When a currently traveling car sees a red light, it will calculate
\emph{where} it needs to stop, and \emph{when} it will come to a stop. This will be done using a deceleration model
similar to \cite{deceleration}. If the light turns to green, the car instead needs to start accelerating (using one of
the models mentioned above). The model will adapt to light changes during movement by recalculating its estimated
exit time of the system.

@@

We first concern ourselves with finding an input distribution for cars entering the system. In our model, we'll only
consider basic aspects of a car: when it enters the system, and it's intended destination (turning left or right at
12th street or going straight). We will assume that all cars have the same speed entering the system, and that they
have the same length. These values can be calculated from the NGSIM data set \cite{ngsim}.

The distribution of car arrival is very important, but has been difficult to model.
